Appendix

### 2025-10-15 manuscript_rmarkdown/manuscript.Rmd
Update manuscript tex.
It compiles properly.
Replace IQR for standardisation with Qn estimator.

Then the log-likelihood function of the location- and scale- invariant Yeo-Johnson power transformation is defined as:
\begin{equation}
\label{eqn:yeo-johnson-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{YJ}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
\end{definition}

@@

\begin{equation}
\label{eqn:yeo-johnson-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{l}_{\text{rYJ}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi_{\text{YJ}}^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \left( \sum_{i=1}^n w_i \right) \log s + (\lambda - 1) \sum_{i=1}^n w_i \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
\end{definition}

@@

2. robust scaling: $x^{\prime}_{i} = \left(x_i - \text{median}\left(\mathbf{X}\right) \right) / \text{IQR}\left(\mathbf{X}\right)$,
   with $\text{IQR}$ representing the interquartile range of $\mathbf{X}$.

>>>>

Then the log-likelihood function of the location- and scale- invariant Yeo-Johnson power transformation is defined as:
\begin{equation}
\label{eqn:yeo-johnson-invariant-log-likelihood}
\begin{split}
\mathcal{L}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi_{YJ}^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
\end{definition}

@@

\begin{equation}
\label{eqn:yeo-johnson-weighted-invariant-log-likelihood}
\begin{split}
\mathcal{L}_{\text{rYJ}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi_{\text{YJ}}^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \left( \sum_{i=1}^n w_i \right) \log s + (\lambda - 1) \sum_{i=1}^n w_i \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
\end{definition}

@@

2. robust scaling: $x^{\prime}_{i} = \left(x_i - \text{median}\left(\mathbf{X}\right) \right) / Q_n\left(\mathbf{X}\right)$,
   with $Q_n$ representing the robust $Q_n$ scale estimator of $\mathbf{X}$ [@Croux1992-zz; @Rousseeuw1993-it].

### 2025-10-15 manuscript_rmarkdown/manuscript_appendix.Rmd
Replace IQR for standardisation with Qn estimator.

\midrule
none                                  & 16.5 & 110.1 & 54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  30.0 & 55.3 & 319.0 & 32.2 \\
conventional (z-score norm.)          & 11.5 &  19.3 & 49.0 & 326.2 & 33.3 \\
conventional (robust scaling)         & 11.3 &  31.8 & 53.3 & 324.5 & 32.2 \\
Raymaekers-Rousseeuw                  & 11.5 & 136.7 & 47.7 & 315.1 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.2 & 214.5 & 57.4 & 326.2 & 33.3 \\
Raymaekers-Rousseeuw (robust scaling) & 11.7 & 281.3 & 57.0 & 324.5 & 32.0 \\
invariant                             &  8.8 &  12.2 & 44.0 & 326.4 & 26.8 \\
robust invariant                      &  9.3 &  30.2 & 55.8 & 308.1 & 22.0 \\

@@

\midrule
conventional                          & 2.0 & -0.7 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 & -1.7 & -0.1 &  1.3 &  0.6 \\
conventional (robust scaling)         & 1.3 &  0.0 &  0.2 &  1.4 &  0.4 \\
Raymaekers-Rousseeuw                  & 2.0 &  1.1 &  0.8 & 95.4 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.3 &  1.4 &  1.0 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw (robust scaling) & 1.4 &  1.3 &  1.0 &  1.4 &  0.4 \\
invariant                             & 1.3 &  0.2 & -1.3 &  1.5 &  0.5 \\
robust invariant                      & 1.3 & -0.3 &  1.0 &  1.1 &  0.3 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\midrule
none                                  & 16.5 & 110.1 &  54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  33.5 &  55.7 & 318.9 & 32.2 \\
conventional (z-score norm.)          & 12.9 &  44.5 &  58.8 & 305.3 & 27.3 \\
conventional (robust scaling)         & 12.9 &  44.7 &  59.0 & 305.3 & 27.3 \\
Raymaekers-Rousseeuw                  & 11.5 & 127.1 &  47.6 & 314.8 & 32.2 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & 13.1 &  54.8 & 127.5 & 510.2 & 23.6 \\
Raymaekers-Rousseeuw (robust scaling) & 18.9 & 100.2 & 113.7 & 510.2 & 23.6 \\
invariant                             & 11.6 &  28.0 &  48.4 & 311.8 & 27.3 \\
robust invariant                      & 12.8 & 150.1 &  60.5 & 646.0 & 27.4 \\

@@

conventional                          & 1.9 & -0.5 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 &  0.1 &  0.2 &  1.2 &  0.5 \\
conventional (robust scaling)         & 1.2 &  0.1 &  0.1 &  1.2 &  0.5 \\
Raymaekers-Rousseeuw                  & 1.9 &  1.1 &  0.8 & 95.9 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.2 &  0.6 & -0.5 &  0.6 &  0.3 \\
Raymaekers-Rousseeuw (robust scaling) & 0.9 &  1.0 & -0.5 &  0.6 &  0.3 \\
invariant                             & 1.7 & -1.0 & -0.7 &  1.9 &  0.5 \\
robust invariant                      & 1.3 &  1.2 &  1.1 &  0.4 &  0.1 \\

>>>>

\midrule
none                                  & 16.5 & 110.1 & 54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  30.0 & 55.3 & 319.0 & 32.2 \\
conventional (z-score norm.)          & 11.5 &  19.3 & 49.0 & 326.2 & 33.3 \\
conventional (robust scaling)         & 11.3 &  33.3 & 55.9 & 326.4 & 31.5 \\
Raymaekers-Rousseeuw                  & 11.5 & 136.7 & 47.7 & 315.1 & 32.2 \\
Raymaekers-Rousseeuw (z-score norm.)  & 13.2 & 214.5 & 57.4 & 326.2 & 33.3 \\
Raymaekers-Rousseeuw (robust scaling) & 13.4 & 203.0 & 56.9 & 326.4 & 31.5 \\
invariant                             &  8.8 &  12.2 & 44.0 & 326.4 & 26.8 \\
robust invariant                      &  9.3 &  30.2 & 55.8 & 308.1 & 22.0 \\

@@

\midrule
conventional                          & 2.0 & -0.7 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 & -1.7 & -0.1 &  1.3 &  0.6 \\
conventional (robust scaling)         & 1.2 &  0.0 &  0.3 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw                  & 2.0 &  1.1 &  0.8 & 95.4 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.3 &  1.4 &  1.0 &  1.3 &  0.6 \\
Raymaekers-Rousseeuw (robust scaling) & 1.3 &  1.2 &  1.0 &  1.3 &  0.6 \\
invariant                             & 1.3 &  0.2 & -1.3 &  1.5 &  0.5 \\
robust invariant                      & 1.3 & -0.3 &  1.0 &  1.1 &  0.3 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

@@

\midrule
none                                  & 16.5 & 110.1 &  54.5 & 328.4 & 48.0 \\
conventional                          & 11.5 &  33.5 &  55.7 & 318.9 & 32.2 \\
conventional (z-score norm.)          & 12.9 &  44.5 &  58.8 & 305.3 & 27.3 \\
conventional (robust scaling)         & 12.9 &  44.7 &  59.0 & 305.3 & 27.3 \\
Raymaekers-Rousseeuw                  & 11.5 & 127.1 &  47.6 & 314.8 & 32.2 \\ 
Raymaekers-Rousseeuw (z-score norm.)  & 13.1 &  54.8 & 127.5 & 510.2 & 23.6 \\
Raymaekers-Rousseeuw (robust scaling) & 13.1 & 100.2 &  44.9 & 423.2 & 23.6 \\
invariant                             & 11.6 &  28.0 &  48.4 & 311.8 & 27.3 \\
robust invariant                      & 12.8 & 150.1 &  60.5 & 646.0 & 27.4 \\

@@

conventional                          & 1.9 & -0.5 & -0.1 & 62.1 & -0.5 \\
conventional (z-score norm.)          & 1.2 &  0.1 &  0.2 &  1.2 &  0.5 \\
conventional (robust scaling)         & 1.2 &  0.1 &  0.1 &  1.2 &  0.5 \\
Raymaekers-Rousseeuw                  & 1.9 &  1.1 &  0.8 & 95.9 & -0.5 \\
Raymaekers-Rousseeuw (z-score norm.)  & 1.2 &  0.6 & -0.5 &  0.6 &  0.3 \\
Raymaekers-Rousseeuw (robust scaling) & 1.2 &  1.0 &  0.8 &  0.7 &  0.3 \\
invariant                             & 1.7 & -1.0 & -0.7 &  1.9 &  0.5 \\
robust invariant                      & 1.3 &  1.2 &  1.1 &  0.4 &  0.1 \\
